\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrit of section 5

Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection-based reconciliation in practice. Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}. Our motivation in this study is twofold. First, we demonstrate the implications of Theorem~\ref{th:distred} {\color{blue} and Theorem~\ref{th:gmint}} by comparing reconciled and base forecasts. In contrast to previous studies, we consider individual periods {\color{blue} as well as} compute averages over a rolling window. Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.

@@

The top panel of Figure~\ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first level of the geographical hierarchy. The panels below show some selected series from the second-level zones and the bottom-level regions. The plots display the diversity of time series features, within but also between levels. For example, noticeable at the first level is the asynchronous seasonal pattern between the Northern Territory and the other states. For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February. This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season. Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being much noisier compared to the series from levels above. This of course highlights the importance of modelling series at all levels without any loss of valuable information. We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December 2002. We replaced this observation with the average overnight trips on December 2001 and December 2003 for the same destination.

@@

\subsection{Comparison to Base Forecasts}\label{sec:comparebase}

@@

{\color{red} I think the flow here is a bit confusing. I see that we need to talk about the loss functions before the reconciliation methods because of Spend-WLS. I suggest the following. We first introduce the three typical reconciliation methods - OLS, Structural-WLS and MinT and move the paragraph that introduces these above. Then when we introduce the loss functions we introduce in the second paragraph, starting ``The second choice'' Spend-WLS. I've re-written 5.2 based on this thought and called it -George in the end. See what do you think? Please delete appropriately.}

{\color{blue} For each replication {\color{red} and for method $q$,- I don't think we need this here - $q$ is defined over the page} we compute three loss functions.  The first is the total squared error (TSE), computed as
	\begin{equation}
	\label{eq:tse}
	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
	\end{equation}
	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a squared generalised Euclidean distance of the form
\begin{equation*}
	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
	\end{equation*}
	We consider two choices of weights.  The first is the inverse of the number of bottom-level series included in forming a specific aggregate.  For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.  The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.  Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.  As such we refer to WLS based on these weights as `Structural-WLS' and the loss function based on these weights as `Structural-WSE'.

	The second choice of weights is motivated by our empirical example.  In addition to visitor numbers per region, we also have access to data on average spend per region.  In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.  By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers. We refer to WLS based on these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.
}

After obtaining the base forecasts these are reconciled using four different projection methods: OLS, {\color{blue} Structural-WLS, Spend-WLS  and MinT.   For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate  $\bm{\Sigma}$. The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$. }

\clearpage
\subsection*{Comparison to Base Forecasts - George}\label{sec:comparebase}

After obtaining the base forecasts these are reconciled using various projection methods. In particular: OLS reconciliation; WLS reconciliation using structural scaling introduced by \cite{AthEtAl2017} which we refer to as Structural-WLS; and MinT using the shrinkage estimator of \cite{Schafer2005} to estimate  $\bm{\Sigma}$. The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$.

{\color{blue} For each method we compute three loss functions.  The first is the total squared error (TSE), computed as
	\begin{equation}
	\label{eq:tse}
	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
	\end{equation}
	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a squared generalised Euclidean distance of the form
\begin{equation*}
	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
	\end{equation*}
	We consider two choices of weights.  The first is the inverse of the number of bottom-level series included in forming a specific aggregate.  For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.  The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.  These are the weights used in the Structural-WLS reconciliation approach introduced in the previous paragraph. As such we refer to the loss function based on these weights as `Structural-WSE'.

	The second choice of weights is motivated by our empirical example.  In addition to visitor numbers per region, we also have access to data on average spend per region.  In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.  By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers. Using these weights we introduce an alternative WLS reconciliation approach which we refer to as `Spend-WLS'. Correspondingly we refer to the loss function based on these weights as `Spend-WSE'.
}

{\color{red} My rewrite of 5.2 ends here}

@@

The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative mean total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation}
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}. {\color{red} You said you commented on statistical significance but I cannot see it. I wonder what the Nemenyi matrix tests will look like here. Maybe these will show some stat significances worth reporting. --- Ok I see it is in the caption but the sentence needs fixing. Maybe it is best to have in the text rather than the caption.}
}

\begin{table}[ht]
	\centering
{\color{blue}	
	\begin{tabular}{lrrrrrr}
		\hline
		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\
		\hline
		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\
		Structural-WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\
		Spend-WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\
		\hline
    \end{tabular}
}
	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.  The lowest mean is always provided by MinT, for Structural-WSE, the average loss for MinT is significantly than every other method.}}
	\label{tab:lossVmethods}
\end{table}

@@

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts. \footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons I HOPE. Doing those today. We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method $q$. Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}

\begin{table}[!b]
{\color{blue}
\caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
\label{tab:Results_MSE}
\setlength{\tabcolsep}{7pt}
\centering
  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
    \multicolumn{3}{c}{Box-Cox Transformation}\\
    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
              & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
              & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
    \bottomrule
  \end{tabular}
}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased base forecasts from the same reconciliation method.}

>>>>

Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection-based reconciliation in practice. Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}. Our motivation in this study is twofold. First, we demonstrate the implications of Theorems~\ref{th:distred}{\color{blue},~\ref{th:gdistred} and~\ref{th:gmint}} by comparing reconciled and base forecasts. In contrast to previous studies, we consider individual periods {\color{blue} as well as} compute averages over a rolling window. Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.

@@

The top panel of Figure~\ref{fig:States_Zones_Regs_TSplots} shows time plots for the six states and Northern Territory, hence the first level of the geographical hierarchy. The panels below show some selected series from the second-level zones and the bottom-level regions. The plots display the diversity of time series features, within but also between levels. For example, noticeable at the first level is the asynchronous seasonal pattern between the Northern Territory and the states. For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February. This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the north during its dry winter-season rather than the wet summer season. Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being much noisier compared to the series from levels above. This of course highlights the importance of modelling series at all levels without any loss of valuable information. We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December 2002. We replaced this observation with the average overnight trips on December 2001 and December 2003 for the same destination.

@@

\subsection*{Comparison to Base Forecasts}\label{sec:comparebase}

@@

After obtaining the base forecasts these are reconciled using various projection methods. In particular: OLS reconciliation, MinT and WLS reconciliation with two different choices of weights that are defined below.  For MinT the shrinkage estimator of \cite{Schafer2005} is used to estimate  $\bm{\Sigma}$. It is given by $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
	\begin{equation*}
	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
	\end{equation*}
	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$.

{\color{blue} For each method we compute three loss functions.  The first is the total squared error (TSE), computed as
	\begin{equation}
	\label{eq:tse}
	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
	\end{equation}
	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
This loss function is $L^2$, the square of the usual Euclidean distance described in Section~\ref{sec:Reconciliation}. We also consider weighted squared error
\begin{equation*}
	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n w_i\left( (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
	\end{equation*}
	which is a loss functions based on a squared generalised Euclidean distance $L_{\bm{W}}^2$, with diagonal $\bm{W}$.  We consider two choices of weights.  The first is the squared inverse of the number of bottom-level series included in forming a specific aggregate.  For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.  The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.  Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.  As such we refer to the reconciliation method that uses these weights as `Stuctural-WLS' and the loss function based on these weights as `Structural-WSE'.

	The second choice of weights is motivated by our empirical example.  In addition to visitor numbers per region, we also have access to data on average spend per region.  In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.  By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue, measured in dollars, rather than raw tourist numbers.  We refer to the reconciliation method that uses these weights as `Stuctural-WLS' and the loss function based on these weights as `Structural-WSE'.
}

@@

The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).  Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative mean total squared error (RMTSE) is defined as
\begin{equation}
\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
\end{equation}
where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.  In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.  Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.  This is precisely what would be expected from Theorem~\ref{th:gmint}. For Structural-WSE, a Diebold Mariano test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.  Strutural-WSE stablises this effect.}}.

\begin{table}[ht]
	\centering
{\color{blue}	
	\begin{tabular}{lrrrrrr}
		\hline
		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\
		\hline
		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\
		Structural-WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\
		Spend-WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\
		\hline
    \end{tabular}
}
	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}}
	\label{tab:lossVmethods}
\end{table}

@@

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$. Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}

\begin{table}[!b]
{\color{blue}
\caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
\label{tab:Results_MSE}
\setlength{\tabcolsep}{7pt}
\centering
  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
    \multicolumn{3}{c}{Box-Cox Transformation}\\
    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
              & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
              & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
    \bottomrule
  \end{tabular}
}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased forecasts from the same reconciliation method (same row).}
